Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-21 JASA-template.tex
Small fix.

For the precision term $1/\sigma^2$, a natural choice of prior is the gamma distribution
as it allows the control of both the location and the scale of the precision.
%%% MT to TB: why not simply say the prior is exponential?
To ensure that the prior is able to represent the data, we consider $b=1$ and 
fix $a$ so that it represents the prior mean of the precision.
%%% MT to TB: "no prior information" seems a bit misleading here? I suggest removing
% In cases where we have no prior information,
We can simply consider a large enough value for $a$
%%% MT to TB: the next phrase is confusing... do you mean to say "with probability ..." (not sure what that is for [0,2a], but true value has probability of about 95% to be contained in [0,3a] for the exponential since 1-exp(-3) is about 95%))
so that the interval
$[0, 2a]$ contains the true value of the precision.
We use a beta prior to
model our uncertainty about
the selection probabilities $\pi_j$ where  $q_j$ represents our prior expectation of the selection probability ($\pi_j$) and $s$ acts as 
a concentration parameter.
For the causal effect, we want to use a Gaussian distribution that 
matches the scale of the noise term. Therefore, we consider $\beta_T\sim \normal(0,\sigma^2)$.

>>>>

For the precision term $1/\sigma^2$, a natural choice of prior is the gamma distribution
as it allows the control of both the location and the scale of the precision.
%%% MT to TB: why not simply say the prior is exponential?
To ensure that the prior is able to represent the data, we consider $b=1$ and 
fix $a$ so that it represents the prior mean of the precision.
%%% MT to TB: "no prior information" seems a bit misleading here? I suggest removing
% In cases where we have no prior information,
We can simply consider a large enough value for $a$
%%% MT to TB: the next phrase is confusing... do you mean to say "with probability ..." (not sure what that is for [0,2a], but true value has probability of about 95% to be contained in [0,3a] for the exponential since 1-exp(-3) is about 95%))
so that the interval
$[0, 2a]$ contains the true value of the precision.
We use a beta prior to
model our uncertainty about
the selection probabilities $\pi_j$ where  $q_j$ represents our prior expectation of $\pi_j$ and $s$ acts as 
a concentration parameter.
For the causal effect, we want to use a Gaussian distribution that 
matches the scale of the noise term. Therefore, we consider $\beta_T\sim \normal(0,\sigma^2)$.
